---
title: "Addtional Analysis with SfC and CQC data"
author: "Meng Ye"
date: "2/19/2023"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r contr}
# environment setup to run ordered logit properly
options(contrasts = rep("contr.treatment", 2))
```


This chunk loads all the packages to use

```{r load package, message=FALSE, warning=FALSE}
#packages for ordered logit
library(tidyverse) # package for data cleaning and plotting
library(readxl) # package for reading excel file
library(broom) # extracting model summary as data frame
library(modelsummary) # deriving model tables
library(scales) # label percent
library(lubridate) # working with dates
library(marginaleffects) #to calculate marginal effects

library(ordinal) # package for ordinal logit regression

```



## Data Preparation

First, import the sampled and coded data set

```{r import data, message=FALSE, warning=FALSE}
#import the raw data file
socialcare_sk <- read_csv("data/cqc_sfc_cleaned.csv")
```


```{r}
socialcare <- socialcare_sk %>% 
# recode legal form types to be more readable / easier to present
  mutate(inherited = ifelse(inherited == "Y", TRUE, FALSE),
         rating = recode(rating, 
                         "Insufficient evidence to rate" = "NA",
                         "Requires improvement" = "Req improv")) %>% 
  # set the order of the values in the factors 
  mutate(form = ordered(form, levels = c("FPO", "NPO", "GOV", "CIC", "IND")),
         
  # assume the order of the ratings as follows but need to double check with the source 
         rating = ordered(rating, levels = c("Inadequate","Req improv", "Good", "Outstanding"))) %>%
  
  # adding the rating data coded as numerical
  mutate(rating_num = case_when(rating == "Inadequate" ~ 1,
                                rating == "Req improv" ~ 2,
                                rating == "Good" ~ 3,
                                rating == "Outstanding" ~ 4)) %>% 
  
  mutate(category = case_when(primary_cat == "Community based adult social care services" ~ "community",
                              primary_cat == "Residential social care" ~ "residential",
                              TRUE ~ as.character(NA)),

         # deriving year column and dummy variable for before_covid
         year = year(publication_date),
         after_covid = ifelse(year >= 2020, TRUE, FALSE),
         before_covid = ifelse(year <= 2019, TRUE, FALSE)) %>%

  # converting the ordinal variable to numerical 
  mutate(rating_num = case_when(rating == "Inadequate" ~ 1,
                                rating == "Req improv" ~ 2,
                                rating == "Good" ~ 3,
                                rating == "Outstanding" ~ 4)) %>% 
  # derive the rating dummy
  mutate(rating_higher = ifelse(rating_num > 2, 1, 0))
```



## Running OLS models 

The OLS models and the ordered logit models can be written as follows

$rating_{numerical} = \beta_0 + \beta_1form + \beta_2category+ \beta_3region + \beta_4inherited + u$

$log-odds(rating_{ordinal} \leq j) = \beta_{j0} + \beta_1form + \beta_2category+ \beta_3region + \beta_4inherited + u$

In this section, we first run the OLS models. In the OLS models, we kind of "cheat" R by treating the four rating levels with orders as if they are numbers 1-4. There are the flowing reasons that we report the results from OLS models, even though the more suitable methods should be ordered logit models, about which we will discuss in a while.

1) The purpose of fitting OLS models is to use them as benchmarks. 
2) Since there are issues like heteroscedasticity, the standard errors calculated are not reliable. But the correlation relationships between the independent variables and dependent variables are still true. So the results are still informative 
3) Plus, compared with the ordered logit models we run later, the results are more straightforward, and more easily give us intuition about how different legal forms of social care providers impact the service quality ratings. 
4) The OLS models are intended to be compared with the ordered logit models. As shown later, the results are generally consistent between the two model families, confirming that our model specification is robust between different models.



### OLS with the sub-domain ratings one by one 

```{r}
# run the model loops with nest() method
models_ols <- socialcare %>% 
  group_by(domain) %>% 
  nest()%>% 
  mutate(ols_models = map(data, 
                          ~lm(rating_num ~ form + age + capacity +
                              category + region + inherited , 
                              data = .x))) %>% 
  mutate(results = map(ols_models, ~tidy(.x, conf.int = TRUE))) %>% 
  pull(ols_models, name = domain)
```

```{r}
# run the model loops with nest() method
# add before_covid as control
# add also interaction term
table_ols <- modelsummary(models_ols, statistic = "({p.value}) {stars}")
table_ols
```



```{r}
# run the model loops with nest() method
# add after_covid as control
models_ols_covid <- socialcare %>% 
  group_by(domain) %>% 
  nest()%>% 
  mutate(ols_models = map(data, 
                          ~lm(rating_num ~ form + after_covid + 
                              category + region + inherited, 
                              data = .x))) %>% 
  mutate(results = map(ols_models, ~tidy(.x, conf.int = TRUE))) %>% 
  pull(ols_models, name = domain) 
```


```{r}
table_ols_covid <- modelsummary(models_ols_covid, statistic = "({p.value}) {stars}")
table_ols_covid
```



## ordered logit models 


### whole model without control 

```{r }
model_order_overall <- clm(rating ~ form + category + region + inherited,
                data = filter(socialcare, domain == "Overall"),
                link = "logit")
model_order_safe <- clm(rating ~ form + category + region + inherited + age + capacity,
                data = filter(socialcare, domain == "Safe"),
                link = "logit")
model_order_effective <- clm(rating ~ form + category + region + inherited + age + capacity,
                data = filter(socialcare, domain == "Effective"),
                link = "logit")
model_order_caring <- clm(rating ~ form + category + region + inherited + age + capacity,
                data = filter(socialcare, domain == "Caring"),
                link = "logit")
model_order_well_led <- clm(rating ~ form + category + region + inherited + age + capacity,
                data = filter(socialcare, domain == "Well-led"),
                link = "logit")
model_order_responsive <- clm(rating ~ form + category + region + inherited + age + capacity,
                data = filter(socialcare, domain == "Responsive"),
                link = "logit")
```




```{r}
ordinal_models <- modelsummary(list("overall" = model_order_overall, "safe" = model_order_safe, 
                                    "effective" = model_order_effective, "caring"= model_order_caring, 
                                    "well-led" = model_order_well_led, "responsive" = model_order_responsive),
                               coef_omit = "region", exponentiate = F,
                               statistic = "({p.value}) {stars}")
ordinal_models
```



```{r}
ordinal_models_exp <- modelsummary(list("overall" = model_order_overall, "safe" = model_order_safe, 
                                    "effective" = model_order_effective, "caring"= model_order_caring, 
                                    "well-led" = model_order_well_led, "responsive" = model_order_responsive),
                               coef_omit = "region", exponentiate = T,
                               statistic = "({p.value}) {stars}")
ordinal_models_exp
```


### whole model with control 


```{r }
model_order_overall_covid <- clm(rating ~ form + after_covid + age + capacity + 
                                   category + region + inherited,
                data = filter(socialcare, domain == "Overall"),
                link = "logit")
model_order_safe_covid <- clm(rating ~ form + after_covid + age + capacity + 
                                category + region + inherited,
                data = filter(socialcare, domain == "Safe"),
                link = "logit")
model_order_effective_covid <- clm(rating ~ form + after_covid + age + capacity + 
                                     category + region + inherited,
                data = filter(socialcare, domain == "Effective"),
                link = "logit")
model_order_caring_covid <- clm(rating ~ form + after_covid + age + capacity + 
                                  category + region + inherited,
                data = filter(socialcare, domain == "Caring"),
                link = "logit")
model_order_well_led_covid <- clm(rating ~ form + after_covid + age + capacity + 
                                    category + region + inherited,
                data = filter(socialcare, domain == "Well-led"),
                link = "logit")
model_order_responsive_covid <- clm(rating ~ form + after_covid + age + capacity + 
                                      category + region + inherited,
                data = filter(socialcare, domain == "Responsive"),
                link = "logit")
```


```{r}
ordinal_models_covid <- modelsummary(list("overall" = model_order_overall_covid, "safe" = model_order_safe_covid, 
                                    "effective" = model_order_effective_covid, "caring"= model_order_caring_covid, 
                                    "well-led" = model_order_well_led_covid, "responsive" = model_order_responsive_covid),
                               coef_omit = "region", exponentiate = F,
                               statistic = "({p.value}) {stars}")
ordinal_models_covid
```


```{r}
ordinal_models_covid_exp <- modelsummary(list("overall" = model_order_overall_covid, "safe" = model_order_safe_covid, 
                                    "effective" = model_order_effective_covid, "caring"= model_order_caring_covid, 
                                    "well-led" = model_order_well_led_covid, "responsive" = model_order_responsive_covid),
                               coef_omit = "region", exponentiate = T,
                               statistic = "({p.value}) {stars}")
ordinal_models_covid_exp
```


























