---
title: "Data Cleaning for Skills for Care Data"
author: "Meng Ye"
date: "3/14/2024"
output:
  html_document: default
  pdf_document: default
  word_document: default
---
Updated 3/14/2024, use more accurate skills for care variables for analysis

### Setting up
```{r load package, message=FALSE, warning=FALSE}
library(tidyverse) # package for data cleaning and plotting
library(readxl) # package for reading excel file
library(broom) # extracting model summary as data frame
library(modelsummary) # deriving model tables
library(scales) # label percent
library(lubridate) # working with dates
library(here) # managing paths
```

```{r contr}
# environment setup to run ordered logit properly
options(contrasts = rep("contr.treatment", 2))
```

## Import data 

```{r import data, message=FALSE, warning=FALSE}
#import the raw data file
cqc_skills <- read_excel(here("data","SfC_CQC.xlsx")) # CQC data with bridging column of SfC establishment id curated by Skills for Care
skills_raw <- read_csv(here("data","Skills_raw.csv")) # raw Skills for Care organizational data
```


## Pivo for CQC_skills (cqc data with SfC establishmentid)

```{r}
#select the CQC data that has Skills for Care establishment id
CQC_sub <- cqc_skills %>% 
  filter(!is.na(establishmentid)) %>% 
#restructure to wide data (1 row for each establishment id)
  pivot_wider(names_from = domain, values_from = rating) %>% 
  mutate(form = ifelse(form == "NA", NA, form))

head(CQC_sub)
```

```{r}
CQC_sub %>% 
  summarize(all_rows = n(),
            unique_rows = n_distinct(establishmentid))
```

This results show that some facilities have more than 1 rating group. After inspecting the raw CQC data, it turned out multiple sets of ratings for the same location are for different service groups.  


## Data Cleaning for Skills for Care data
### Select Columns 

```{r}
#write variable name list
columns <- c("ParentSubSingle", "isparent", "estabcreateddate",  #basic info
             "Starters_Leavers_FILTER", "totalstarters", "totalleavers", #staff
             "totalstaff", "totalvacancies","ORGWRKS", "ORGWRKSGP","ESTABWRKS", #staff
             "esttype",  "mainstid", "MAINSERGP1", "MAINSERGP2") #service descriptions
             
```

Notes for some variables:

`ParentSubSingle`: values: 0, 1, 2. Does not say which is parent/sub/single. It is observed 2 corresponds to `isparent = 1", so should be parent. 


`Starters_Leavers_FILTER`: Flag to define if a workplace has reliable starters or leavers information.
1 = Include, 0 = Exclude. 

`ORGWRKS`: Sum of totalstaff **across** the organisation.

`ORGWRKSGP`: Grouping of ORGWRKS

  Value	 Label
  -1	   Not allocated
  991	   Micro (1 to 9)
  992	   Small (10 to 49)
  993	   Medium (50 to 249)
  994	   Large (250 or more)

`esttype`: sector of the workplace

`mainstid`: The main service provided by the workplace

`totalstarters` and `totalleavers`: Total number of permanent and temporary staff that started/left in the previous 12 months.


```{r select columns}
skills_selected <- skills_raw %>% 
  select(establishmentid, all_of(columns), starts_with("jr28"), starts_with("jr29"),
         matches("^st.*cap$"), matches("^st.*util$"))
```


- "jr" codes

Code	Label

28	**Any job role**. This is the sum of all job roles submitted by the establishment.

29	**Any direct care role**. This is the sum of all direct care roles submitted by the establishment. (Note: this variable may be more directly related to service quality)

30	Any manager/supervisor role. This is the sum of all manager/supervisor roles submitted by the establishment.

31	Any regulated profession role. This is the sum of all regulated profession roles submitted by the establishment.

32	Any other roles. This is the sum of all other roles, those not included in groups 29,30 and 31, submitted by the establishment.

1	Senior Management

2	Middle Management

3	First Line Manager

4	Registered Manager

5	Supervisor

6	Social Worker

7	Senior Care Worker

8	Care Worker

9	Community Support and Outreach Work

10	Employment Support

11	Advice Guidance and Advocacy

15	Occupational Therapist

16	Registered Nurse

17	Allied Health Professional

22	Technician

23	Other care-providing job role

24	Managers and staff in care-related but not care-providing roles

25	Administrative or office staff not care-providing

26	Ancillary staff not care-providing

27	Other non-care-providing job roles

34	Activities worker or co-ordinator

35	Safeguarding and reviewing officer

36	Occupational therapist assistant

37	Nursing Associate

38	Nursing Assistant

39	Assessment officer

40	Care co-ordinator

41	Care navigator

42	Any Childrens/young peoples job role



## Exploring the strucutre of Skills for Care data

Use this small dataset to check if each establishment ID has multiple rows

```{r}
skills_raw %>% 
  select(establishmentid) %>% 
  summarise(count = n(),
            count_unqice = n_distinct(establishmentid))

```

In the Skills for Care data set, each `establishmentid` only corresponds to 1 row data.


## Merge data and derive new variables

### coding section

```{r}
# merge and recode data
merged_wide <- CQC_sub %>% 
  left_join(skills_selected, by = "establishmentid") %>% 
  mutate(main_service_type = factor(mainstid),
         main_group1 = factor(MAINSERGP1),
         main_group2 = factor(MAINSERGP2),
         
         main_service_group = case_when(
           main_group1 == "1" ~ "Adult residential",
           main_group1 == "3" ~ "Adult domicilary", 
           TRUE ~ as.character(NA)),
         
# derive truncated service types (where CICs exist) see table 1
         service_type_selected = case_when(
           main_service_type == "1"  ~ "care home w/ nursing",
           main_service_type == "2"  ~ "care home w/o nursing",
           main_service_type == "8"  ~ "Domicilary Care",
           main_service_type == "55" ~ "Supported Living",
           # dropped 61 -- community based for learning disability
           TRUE ~ as.character(NA)),

# recode size type to be more readable
         size_type = case_when(
           ORGWRKSGP == -1  ~ as.character(NA),
           ORGWRKSGP == 991 ~ "micro",
           ORGWRKSGP == 992 ~ "small",
           ORGWRKSGP == 993 ~ "medium",
           ORGWRKSGP == 994 ~ "large",
           TRUE ~ as.character(NA)),
# derive age of the organization
        start_date = dmy(estabcreateddate),
        age = 2024-year(start_date)
) %>% 
  mutate(total_leavers = ifelse(totalleavers < 0, NA, totalleavers),
         total_starters = ifelse(totalleavers < 0, NA, totalstarters))
# recode -1 or -2 to NA for totallevers and totalstarters

```

Check distribution of the data and potential variables 

```{r}
## check the distribution of the data by service type selected
merged_wide %>% 
  group_by(service_type_selected) %>% 
  summarise(count = n())
```

```{r}
# checking how much missing values for total starters
merged_wide %>% 
  group_by(!is.na(total_starters)) %>% 
  summarize(count = n())
```

```{r}
# checking how much missing values for total leavers
merged_wide %>% 
  group_by(!is.na(total_leavers)) %>% 
  summarize(count = n())
```

```{r}
# checking how much missing values for "jr29"
merged_wide %>% 
  group_by(ifelse(jr29flag == 1, TRUE, FALSE)) %>% 
  summarize(count = n())
```




## Derive new variables 


- About the **new** turnover rate


`Employee turnover` rate is the percent of employees who leave a company within a specific time period. Turnover rate is commonly calculated by month, quarter, or year and includes both voluntary and involuntary losses. Monthly and quarterly turnover rates are commonly expressed as averages, while annual turnover rate is usually cumulative.


$$
\text{Employee turnover rate} = \frac{\text{Number of employees who left}}{\text{Average number of employees}} \times 100
$$



$$
\text{Average number of employees} = \frac{\text{(Headcount at the beginning of the timeframe + headcount at the end of the timeframe)}}{2} \\
\phantom{\text{Average number of employees}} = \frac{\text{(headcount at the end of the timeframe + total leavers - total starters + headcount at the end of the timeframe)}}{2}\\
\phantom{\text{Average number of employees}} = \text{(headcount at the end of the timeframe} + \frac{\text{(total leavers - total starters )}}{2}
$$


### New variables could be derived 

count of employees left in last 12 month/latest total staff
by service type, total staff/
number of vacancy - not useful due to a lot of missing value

Any other ideas? Please specify **exact** variable rather than vague concept 

```{r derive new variables}
# derive new variables
merged_recoded_wide <- merged_wide %>% 
# mutate NA only for jr28flag = 1 and jr29 = 1, respectively
  mutate(across(starts_with("jr28"), 
          ~ ifelse(jr28flag == 1, ifelse(is.na(.x), 0, .x), .x))) %>% 
  mutate(across(starts_with("jr29"), 
          ~ ifelse(jr29flag == 1, ifelse(is.na(.x), 0, .x), .x))) %>% 
  mutate(across(starts_with("st"),
         ~ ifelse(is.na(.x), 0, .x))) %>% 
  
  # calculating the old turnover rate, renamed to "turnover1"

  mutate(totalstaff = ifelse(is.na(totalstaff), 0, totalstaff),
         turnover0 = totalleavers/totalstaff * 100,
         turnover0 = ifelse(turnover0 < 0, NA, turnover0),
         turnover0 = ifelse(is.na(turnover0) | turnover0 == Inf, NA, turnover0)) %>% 
  
  # derive the average totalstaff count for the between T-12month and T0
  # and calculate the turnover rate with average total staff

  mutate(average_totalstaff = totalstaff + 1/2 * (total_leavers - total_starters))  %>% 
  mutate(average_totalstaff = ifelse(is.na(average_totalstaff), 0, average_totalstaff),
         turnover = totalleavers/average_totalstaff * 100,
         turnover = ifelse(turnover < 0, NA, turnover),
         turnover = ifelse(is.na(turnover) | turnover == Inf, NA, turnover)) %>% 
  rowwise() %>% 
  mutate(capacity = sum(across(matches("^st.*cap$"))),
         utility = sum(across(matches("^st.*util$")))) %>% 
  ungroup() %>% 
  mutate(staff_level0 = totalstaff/utility,
         staff_level0 = ifelse(staff_level0 == Inf, NA, staff_level0)) %>% 
  mutate(direct_staff = jr29work,
         staff_level = direct_staff/utility,
         staff_level = ifelse(staff_level == Inf, NA, staff_level))
  
```





```{r}
table4 <- datasummary(turnover * service_type_selected *(Mean + SD)~ form,
            data = merged_recoded_wide, fmt = 1, na.rm = T)
table4
```

## Run Toy Models

Prepare data for analysis

```{r}
#pivot longer back
merged_long <- merged_recoded_wide %>% 
  pivot_longer(cols = c(Safe, Effective, Caring, Responsive, `Well-led`, Overall),
               names_to = "domain", values_to = "rating")
```


```{r}
#select relevant columns, rename and relabel 
merged_long_ordered <- merged_long %>% 
# recode legal form types to be more readable / easier to present
  mutate(inherited = ifelse(inherited == "Y", TRUE, FALSE),
         rating = recode(rating, 
                         "Insufficient evidence to rate" = "NA",
                         "Requires improvement" = "Req improv")) %>% 
  # set the order of the values in the factors 
  mutate(form = fct_relevel(form, "FPO"),
         
  # assume the order of the ratings as follows but need to double check with the source 
         rating = ordered(rating, levels = c("Inadequate","Req improv", "Good", "Outstanding"))) %>%
  
  # adding the rating data coded as numerical
  mutate(rating_num = case_when(rating == "Inadequate" ~ 1,
                                rating == "Req improv" ~ 2,
                                rating == "Good" ~ 3,
                                rating == "Outstanding" ~ 4)) %>% 
  
  mutate(category = case_when(primary_cat == "Community based adult social care services" ~ "community",
                              primary_cat == "Residential social care" ~ "residential",
                              TRUE ~ as.character(NA)),

         # deriving year column and dummy variable for before_covid
         year = year(publication_date),
         during_covid = ifelse(year >= 2020, TRUE, FALSE),
         before_covid = ifelse(year <= 2019, TRUE, FALSE)) %>%

  # converting the ordinal variable to numerical 
  mutate(rating_num = case_when(rating == "Inadequate" ~ 1,
                                rating == "Req improv" ~ 2,
                                rating == "Good" ~ 3,
                                rating == "Outstanding" ~ 4)) %>% 
  # derive the rating dummy
  mutate(rating_higher = ifelse(rating_num > 2, 1, 0))

# show first several rows of the data set derived 
head(merged_long_ordered)
```



### Save data

```{r save data}
write_rds(merged_long_ordered, file = here("data","cqc_sfc_cleaned.rds"))  
```




