---
title: "Exploring Skills for Care Data"
author: "Meng Ye"
date: "9/29/2022"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

### Setting up
```{r load package, message=FALSE, warning=FALSE}
#packages for ordered logit
library(ordinal) # package for ordinal logit regression
library(brant) # brant test for the parallel assumption for ordered logit
library(MASS) # models that work with the brant test

library(tidyverse) # package for data cleaning and plotting
library(readxl) # package for reading excel file
library(broom) # extracting model summary as data frame
library(modelsummary) # deriving model tables
library(scales) # label percent
library(lubridate) # working with dates
```

```{r contr}
# environment setup to run ordered logit properly
options(contrasts = rep("contr.treatment", 2))
```

### Import data and exploration 

```{r import data, message=FALSE, warning=FALSE}
#import the raw data file
skills_cqc <- read_excel("data/SfC_CQC.xlsx")
form_full <- read_csv("data/form_full.csv")
```



Check the distribution of different forms
```{r}
form_sub <- skills_cqc %>% 
  group_by(establishmentid) %>% 
  summarise(form = first(form)) %>% 
  count(form)
form_sub
```

Derive the table to compare the distributions
```{r}
form_full <- form_full %>% 
  select(form, 
         count_full = n)
```


```{r}
form_compare <- form_sub %>% 
  filter(form != "NA") %>% 
  select(form, 
         count_sub = n) %>% 
  left_join(form_full, by = "form") %>% 
  mutate(ratio = count_sub/count_full) %>% 
  mutate(pct = label_percent(accuracy = 0.1)(ratio))

form_compare
```


### Run Toy Models

Prepare data for analysis

```{r}
#select relevant columns, rename and relabel 
skills_cqc <- skills_cqc %>% 
# recode legal form types to be more readable / easier to present
  mutate(inherited = ifelse(inherited == "Y", TRUE, FALSE),
         rating = recode(rating, 
                         "Insufficient evidence to rate" = "NA",
                         "Requires improvement" = "Req improv")) %>% 
  # set the order of the values in the factors 
  mutate(form = ordered(form, levels = c("FPO", "NPO", "GOV", "CIC", "IND")),
         
  # assume the order of the ratings as follows but need to double check with the source 
         rating = ordered(rating, levels = c("Inadequate","Req improv", "Good", "Outstanding"))) %>%
  
  # adding the rating data coded as numerical
  mutate(rating_num = case_when(rating == "Inadequate" ~ 1,
                                rating == "Req improv" ~ 2,
                                rating == "Good" ~ 3,
                                rating == "Outstanding" ~ 4)) %>% 
  
  mutate(category = case_when(primary_cat == "Community based adult social care services" ~ "community",
                              primary_cat == "Residential social care" ~ "residential",
                              TRUE ~ as.character(NA)),
         year = year(publication_date),
         before_covid = ifelse(year < 2020, TRUE, FALSE)) 
  

# show first several rows of the data set derived 
head(skills_cqc)
```


Check the distribution by years

```{r}
skills_cqc %>% count(year, before_covid)
```


Check simple differences in means: seems consistent with our earlier findings

```{r}
simple_model <- lm(rating_num ~ form, data = skills_cqc)
summary(simple_model)
```
Running simple difference of means between CIC sub-types

```{r}
simple_cic <- lm(rating_num ~ cic_type, data = skills_cqc)
summary(simple_cic)
```
Again CIC as for-profit with shares (S type) has lower rating, but not significant. The NA group (those are not CICs) difference is significant, as expected. 


### Run the same models as in the full CQC data set

```{r}
# run the model loops with nest() method
model_list <- skills_cqc %>% 
  group_by(domain) %>% 
  nest()%>% 
  mutate(ols_models = map(data, 
                          ~lm(rating_num ~ form + 
                              category + region + inherited + before_covid, 
                              data = .x))) %>% 
  mutate(results = map(ols_models, ~tidy(.x, conf.int = TRUE))) 
```


Derive the OLS results table

I first print out the order of the domain names to match with summary table.

```{r}
models_named <- model_list %>% 
  pull(ols_models, name = domain)
```


```{r}
table_ols <- modelsummary(models_named, statistic = "({p.value}) {stars}")
table_ols
```























