---
title: "Skills-for-care analysis ARNOVA 2023"
author: "Meng Ye"
date: "2023-11-03"
output: html_document
---

```{r contr}
# environment setup to run ordered logit properly
options(contrasts = rep("contr.treatment", 2))
```


This chunk loads all the packages to use

```{r load package, message=FALSE, warning=FALSE}
#packages for ordered logit
library(tidyverse) # package for data cleaning and plotting
library(readxl) # package for reading excel file
library(broom) # extracting model summary as data frame
library(modelsummary) # deriving model tables
library(scales) # label percent
library(lubridate) # working with dates
library(marginaleffects) #to calculate marginal effects
library(ordinal) # package for ordinal logit regression
```



## Data Preparation

First, import the sampled and coded data set

```{r import data, message=FALSE, warning=FALSE}
#import the raw data file
cqc_skills <- read_csv("data/cleaned_sfc_ipw.csv") %>% 
  mutate(form = fct_relevel(form, "FPO"),
         rating = factor(rating),
         Year = factor(year),
         during_covid = after_covid,
         staff_level = staff_level/100)
```





## Detailes about new variables 


- About turnover rate


`Employee turnover` rate is the percent of employees who leave a company within a specific time period. Turnover rate is commonly calculated by month, quarter, or year and includes both voluntary and involuntary losses.


$$
\text{Employee turnover rate} = \frac{\text{Number of employees who left}}{\text{Average number of employees}} \times 100
$$



$$
\text{Average number of employees} = \frac{\text{(Headcount at the begining of the timeframe + headcount at the end of the timeframe)}}{2}
$$




## ordered logit models 

## Modeling on rating withough staff control

```{r }
model_order_overall <- clm(rating ~ form + category + region + during_covid + utility,
                data = filter(cqc_skills, domain == "Overall"),
                link = "logit",
                weights = ipw)

model_order_safe <- clm(rating ~ form + category + region + during_covid + utility,
                data = filter(cqc_skills, domain == "Safe"),
                link = "logit",
                weights = ipw)

model_order_effective <- clm(rating ~ form + category + region + during_covid + utility,
                data = filter(cqc_skills, domain == "Effective"),
                link = "logit",
                weights = ipw)

model_order_caring <- clm(rating ~ form + category + region + during_covid + utility,
                data = filter(cqc_skills, domain == "Caring"),
                link = "logit",
                weights = ipw)

model_order_well_led <- clm(rating ~ form + category + region + during_covid + utility,
                data = filter(cqc_skills, domain == "Well-led"),
                link = "logit",
                weights = ipw)

model_order_responsive <- clm(rating ~ form + category + region + during_covid + utility,
                data = filter(cqc_skills, domain == "Responsive"),
                link = "logit",
                weights = ipw)
```




```{r}
ordinal_models <- modelsummary(list("overall" = model_order_overall, "safe" = model_order_safe, 
                                    "effective" = model_order_effective, "caring"= model_order_caring, 
                                    "well-led" = model_order_well_led, "responsive" = model_order_responsive),
                               coef_omit = "region", exponentiate = F,
                               statistic = "({p.value}) {stars}")
ordinal_models
```






## Modeling on staffing

```{r}
model_staff_overall <- lm(staff_level ~ form + category + region + during_covid + utility,
                data = filter(cqc_skills, domain == "Overall"),
                weights = ipw)

model_staff_safe <- lm(staff_level ~ form + category + region + during_covid + utility,
                data = filter(cqc_skills, domain == "Safe"),
                weights = ipw)

model_staff_effective <- lm(staff_level ~ form + category + region + during_covid + utility,
                data = filter(cqc_skills, domain == "Effective"),
                weights = ipw)

model_staff_caring <- lm(staff_level ~ form + category + region + during_covid + utility,
                data = filter(cqc_skills, domain == "Caring"),
                weights = ipw)

model_staff_well_led <- lm(staff_level ~ form + category + region + during_covid + utility,
                data = filter(cqc_skills, domain == "Well-led"),
                weights = ipw)

model_staff_responsive <- lm(staff_level ~ form + category + region + during_covid + utility,
                data = filter(cqc_skills, domain == "Responsive"),
                weights = ipw)
```


```{r}
staff_models <- modelsummary(list("overall" = model_staff_overall, "safe" = model_staff_safe, 
                                    "effective" = model_staff_effective, "caring"= model_staff_caring, 
                                    "well-led" = model_staff_well_led, "responsive" = model_staff_responsive),
                               coef_omit = "region", exponentiate = F,
                               statistic = "({p.value}) {stars}")
staff_models
```

## Modeling on staffing level direct effects

```{r }
model_staff_direct_overall <- clm(rating ~ form + category + region + during_covid + utility + staff_level,
                data = filter(cqc_skills, domain == "Overall"),
                link = "logit",
                weights = ipw)

model_staff_direct_safe <- clm(rating ~ form + category + region + during_covid + utility + staff_level,
                data = filter(cqc_skills, domain == "Safe"),
                link = "logit",
                weights = ipw)

model_staff_direct_effective <- clm(rating ~ form + category + region + during_covid + utility + staff_level,
                data = filter(cqc_skills, domain == "Effective"),
                link = "logit",
                weights = ipw)

model_staff_direct_caring <- clm(rating ~ form + category + region + during_covid + utility + staff_level,
                data = filter(cqc_skills, domain == "Caring"),
                link = "logit",
                weights = ipw)

model_staff_direct_well_led <- clm(rating ~ form + category + region + during_covid + utility + staff_level,
                data = filter(cqc_skills, domain == "Well-led"),
                link = "logit",
                weights = ipw)

model_staff_direct_responsive <- clm(rating ~ form + category + region + during_covid + utility + staff_level,
                data = filter(cqc_skills, domain == "Responsive"),
                link = "logit",
                weights = ipw)
```




```{r}
staff_direct_models <- modelsummary(list("overall" = model_staff_direct_overall, "safe" = model_staff_direct_safe, 
                                    "effective" = model_staff_direct_effective, "caring"= model_staff_direct_caring, 
                                    "well-led" = model_staff_direct_well_led, "responsive" = model_staff_direct_responsive),
                               coef_omit = "region", exponentiate = F,
                               statistic = "({p.value}) {stars}")
staff_direct_models
```





## Modeling on turnover

```{r}
model_turnover_overall <- lm(turnover ~ form + category + region + during_covid + utility,
                data = filter(cqc_skills, domain == "Overall"),
                weights = ipw)

model_turnover_safe <- lm(turnover ~ form + category + region + during_covid + utility,
                data = filter(cqc_skills, domain == "Safe"),
                weights = ipw)

model_turnover_effective <- lm(turnover ~ form + category + region + during_covid + utility,
                data = filter(cqc_skills, domain == "Effective"),
                weights = ipw)

model_turnover_caring <- lm(turnover ~ form + category + region + during_covid + utility,
                data = filter(cqc_skills, domain == "Caring"),
                weights = ipw)

model_turnover_well_led <- lm(turnover ~ form + category + region + during_covid + utility,
                data = filter(cqc_skills, domain == "Well-led"),
                weights = ipw)

model_turnover_responsive <- lm(turnover ~ form + category + region + during_covid + utility,
                data = filter(cqc_skills, domain == "Responsive"),
                weights = ipw)
```


```{r}
turnover_models <- modelsummary(list("overall" = model_turnover_overall, "safe" = model_turnover_safe, 
                                    "effective" = model_turnover_effective, "caring"= model_turnover_caring, 
                                    "well-led" = model_turnover_well_led, "responsive" = model_turnover_responsive),
                               coef_omit = "region", exponentiate = F,
                               statistic = "({p.value}) {stars}")
turnover_models
```

## Modeling on turnover rate direct effects

```{r }
model_turnover_direct_overall <- clm(rating ~ form + category + region + during_covid + utility + turnover,
                data = filter(cqc_skills, domain == "Overall"),
                link = "logit",
                weights = ipw)

model_turnover_direct_safe <- clm(rating ~ form + category + region + during_covid + utility + turnover,
                data = filter(cqc_skills, domain == "Safe"),
                link = "logit",
                weights = ipw)

model_turnover_direct_effective <- clm(rating ~ form + category + region + during_covid + utility + turnover,
                data = filter(cqc_skills, domain == "Effective"),
                link = "logit",
                weights = ipw)

model_turnover_direct_caring <- clm(rating ~ form + category + region + during_covid + utility + turnover,
                data = filter(cqc_skills, domain == "Caring"),
                link = "logit",
                weights = ipw)

model_turnover_direct_well_led <- clm(rating ~ form + category + region + during_covid + utility + turnover,
                data = filter(cqc_skills, domain == "Well-led"),
                link = "logit",
                weights = ipw)

model_turnover_direct_responsive <- clm(rating ~ form + category + region + during_covid + utility + turnover,
                data = filter(cqc_skills, domain == "Responsive"),
                link = "logit",
                weights = ipw)
```




```{r}
turnover_direct_models <- modelsummary(list("overall" = model_turnover_direct_overall, "safe" = model_turnover_direct_safe, 
                                    "effective" = model_turnover_direct_effective, "caring"= model_turnover_direct_caring, 
                                    "well-led" = model_turnover_direct_well_led, "responsive" = model_turnover_direct_responsive),
                               coef_omit = "region", exponentiate = F,
                               statistic = "({p.value}) {stars}")
turnover_direct_models

```







